Rotation effects on the Lyman-$\alpha$ line morphology in distant galaxies

### 2013-05-17 paper/Analisis.tex
ideas

Previous studies have shown the correlation of the Escape fraction with galctic mass (Lauren 2009 et al, Dayal et al 2010) abundacies and the kinematics of dust. In order to study pure rotational effects in the escape fraction we fixed the dust abundance $\tau_{A}=0.01$ and the galaxy mass. We compute the escape fraction for the models described in Table \ref{table:models}.\\

@@

In Figure \ref{figure:efvsv} we found that in the central distribution
the escape fraction does not change with velocity while it does in the
optical depth. On the other hand for the homogeneous distribution we
found that for higher velocities photons escape easily. The difference
between this two results relly in the fact that in the homogeneous
distribution photons are emitted closer to the escape surface and this
makes this configuration more sensitive to rotation while in the
central configuration the escape fraction depends mainly in the amount
of gas rather than in rotation.

Of great importance is to notest that for the homogeneous distribution the optical depth of $\tau_{H}=10^5$ does not follow the trend known for the others. In order to study this FIG.(CLARA plot)

@@

@@

... Comparison with Verhamme et al. results on the rotation

>>>>

Previous studies have shown the correlation of the Escape fraction with galactic mass (Lauren 2009 et al, Dayal et al 2010) abundacies and the kinematics of dust. In order to study pure rotational effects in the escape fraction we fixed the dust abundance $\tau_{A}=0.01$ and the galaxy mass. We compute the escape fraction for the models described in Table \ref{table:models}.\\

@@

In Figure \ref{figure:efvsv} we found that in the central distribution
the escape fraction does not change with velocity while it does in the
optical depth (See Verhamme 2006, an argument about this). On the other hand for the homogeneous distribution we
found that for higher velocities photons escape easily. The difference
between this two results relly in the fact that in the homogeneous
distribution photons are emitted closer to the escape surface and this
makes this configuration more sensitive to rotation while in the
central configuration the escape fraction depends mainly in the amount
of gas rather than in rotation.

Of great importance is to notest that for the homogeneous distribution the optical depth of $\tau_{H}=10^5$ does not follow the trend known for the others. In order to study this in more detal FIG.(CLARA plot)

@@

..compare steidel et al (2011)

@@

... Comparison with Verhamme et al. results on the rotation
... Compare with Kulas et al (Figure 3), Rotation on the lyman alpha line convert double peak profiles into a single one. comments about rotation with inflows and outflows.
